%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-3pt}}
  }
}

\newcommand{\resumeItemWithoutBullet}[2]{
  \item[]\small{
    \textit{\textbf{#1}{#2 \vspace{-5pt}}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-2pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Nataly Smith}} & Email: \href{mailto:}{nmmsoftware@gmail.com}\\
  \href{https://github.com/astrogirlnim}{Github: https://github.com/astrogirlnim} & Mobile:~~~+1-505-203-6058 \\
  \href{https://www.linkedin.com/in/nataly-smith/}{LinkedIn: linkedin.com/in/nataly-smith/} \\
\end{tabular*}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\vspace{2pt}
\section{\textbf{ABOUT ME}}
\textbf{Senior Software Developer} who specializes in full-stack app development, mathematical modeling, with expertise in cloud technologies/infrastructure and pipeline architecture. Mixing Python, C\#, and custom Bash/Shell scripting for most projects, experience with many other languages and frameworks for professional development. Avid learner of the latest tools and platforms; currently exploring computer hardware, AI, and the global internet.
\vspace{6pt}
\section{\textbf{SKILLS SUMMARY}}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, R, C\#, C, C++, VB, Bash, Matlab, JavaScript, HTML, CSS, SQL, Racket, Lisp}
	\resumeSubItem{Frameworks}{~~~~.NET, WPF/XAML, Scikit, OpenCV, Flask, ReactJS, NextFlow, Luigi}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Docker, Git, PostgreSQL, IIS, Visual Studio, VS Code, Vim}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Google Cloud Platform, Azure, AWS, JIRA,  GitHub, Bitbucket}
    \resumeSubItem{Concepts}{~~~~~~~~OOP, SOLID, Agile Development, Unit and Integration Testing, Mathematical Modeling, Machine Learning}
	\resumeSubItem{Soft Skills}{~~~~~~~Communication, Problem-Solving, Collaboration, Discipline}

\resumeSubHeadingListEnd
\vspace{6pt}
\section{\textbf{RELEVANT EXPERIENCE}}
  \resumeSubHeadingListStart
  \resumeSubheading{Senior Software Developer, CAS Project}{Remote}
    {Bruker NANO, formerly PhenomeX}{March 2023 - Present}
    \resumeItemListStart
          \resumeItem{}{Completed a full-scale Azure DevOps migration in record 3 months by coordinating team efforts, automating migration processes, and creating custom programmatic tools.}
          \resumeItem{}{Expedited application runtime by 75\% with code rewrite, hitting product specifications with an on-time release.}
          \resumeItem{}{Built critical testing functionality ahead of schedule, expediting product release by 2 weeks.}
          \resumeItem{}{Enriched deployment life cycle and scalability through Docker and CI/CD orchestration technologies.}
          \resumeItem{}{Constructed a multi-cloud implementation of Genomic sequencing testing infrastructure.}
      \resumeItemListEnd
    \resumeSubheading{Senior Software Developer, Duomic Project}{Remote}
    {IsoPlexis Corp., a PhenomeX Company}{Dec 2022 - March 2023}
    \resumeItemListStart
          \resumeItem{}{Increased critical application performance by 400\% by leading a re-architecture of existing code.}
          \resumeItem{}{Improved software quality and throughput by implementing DevOps pipeline refactoring and automated testing.}
          \resumeItem{}{Supported interdepartmental teamwork by developing python libraries, custom tools, and high-quality documentation to be shared and referenced.}
          \resumeItem{}{Worked with company leadership to create technology solutions that achieved high-level business goals.}
      \resumeItemListEnd
    \resumeSubheading{Software Developer}{Remote}
    {IsoPlexis Corp., a PhenomeX Company}{Jan 2022 - Dec 2022}
    \resumeItemListStart
        \resumeItem{}{Main developer in creating research tools for next-gen sequencing.}
          \resumeItem{}{Independently developed a web portal that enabled interdepartmental teams to access research tools.}
          \resumeItem{}{Introduced automated unit testing and integration testing into our development packages.}
          \resumeItem{}{Worked with C++ computer vision libraries to improve our sequencing technologies.}
      \resumeItemListEnd
    \resumeSubheading
		{Computer Systems Engineer}{Remote}
		{McMaster-Carr}{Sep 2021 -  Jan 2022}
		\resumeItemListStart
        \resumeItem{}{Improved company knowledge sharing and education by creating an internal communications hub.}
          \resumeItem{}{Worked with established SDLC that involved cross team coordination, testing, and release schedules.}
          \resumeItem{}{Delivered business value by developing website features end to end, including Database Schemas, Business Logic, REST API Implementation, and front-end development.}
          \resumeItem{}{Integrated legacy systems to interface with modern business-critical applications.}
		\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{6pt}
\section{\textbf{EDUCATION}}
\resumeSubHeadingListStart
    \vspace{2pt}\resumeSubheading
      {Yale University}{New Haven, CT}
      {Bachelor of Science - Biomedical Engineering (Focus on Biocomputation); GPA: 3.64}{August 2017 - May 2021}
      \vspace{2pt}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses and Areas of Study:}  Data Structures, Data Science, Analysis of Algorithms, Biomedical Imaging and Device Development, Computation for Research, Mathematical Modeling, High-Performance High-Throughput Programming}, Memory Management}}
\resumeSubHeadingListEnd

%-----------Awards-----------------
\vspace{6pt}
\section{\textbf{HONORS/AWARDS, OTHER}}
\begin{description}[font=$\bullet$]
\item {Runner Up - Yale CBIT (Center for Biomedical Innovation Technology) Healthcare Hackathon - Jan 2021
}
\vspace{-8pt}
\item {Tsai City Accelerator (Yale Tsai Center For Innovative Thinking) program - Nov 2020.}
\vspace{-8pt}
\item {Yale Domestic Summer Award - May 2020.}
\vspace{-8pt}
\item {Cum Laude. Vincent Cordova Diversity Award. National Hispanic Scholar. National Academy of Future Physicians and Medical Scientists Award of Excellence Nominee.}
\vspace{-8pt}
\item {Fluent in English, Spanish, French. }

\end{description}
%-----------PROJECTS-----------------
\vspace{-5pt}
\section{\textbf{RESEARCH EXPERIENCE}}
  \resumeSubHeadingListStart
    \resumeSubheading{Research Intern - Computational Modeling}{Miller-Jensen Lab}
    {Yale School of Engineering and Applied Sciences}{Jan 2020 - May 2021}
    \resumeItemListStart
        \resumeItem{Ensemble of Viruses model of latent HIV gene expression and phenotypes:}{ Supervised by Margaret Elise Bullock, Ph.D.}
          \resumeItem{}{Building predictive models for activation of latent HIV. Computational modeling of an array of phenotype states using a
Network-Free Stochastic Simulator, NFsim.}
          \resumeItem{}{R and MATLAB computational languages used to synthesize HIV expression data for better correspondence analysis. Generation of parameter-phenotype interactome network based on mRNA and protein expression levels.}
      \resumeItemListEnd
    \resumeSubheading
		{Research Intern - Computational Modeling}{Prof. Yi's Group}
		{Department of Oncology, Dell Medical School, Austin, TX}{May 2019 -  Aug 2019}
		\resumeItemListStart
        \resumeItem{Bioinformatics of protein-protein interactions in disease pathology:}{ Independent summer computational research.}
          \resumeItem{}{Visualizing protein-protein interactions using R, ChimeraX, and multiple online bioinformatic tools.}
          \resumeItem{}{Utilization of TCGA High-Throughput Human data for gene enrichment analyses.}
          \resumeItem{}{Applying linear regression, frequency calculations, and original random models to gene expression data.}
		\resumeItemListEnd
  \resumeSubHeadingListEnd

% PUBLICATIONS 
\vspace{2pt}
\section{\textbf{PUBLICATIONS}}
\resumeSubHeadingListStart
\vspace{2pt}
\resumeSubItem{A transcriptional cycling model recapitulates chromatin-dependent features of noisy inducible transcription: }{ Stochastic computational modeling of variable activation of quiescent HIV infections in T cells. Our model more accurately described viral expression variability across cells in response to an upstream stimulus. \\\textbf{DOI:} \href{https://doi.org/10.1371/journal.pcbi.1010152}{https://doi.org/10.1371/journal.pcbi.1010152} 
\\\vspace{2pt}\textbf{Tech} MATLAB, NFSim}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\textbf{PROJECTS}}
\resumeSubHeadingListStart
\vspace{4pt}
\resumeSubItem{Simplifying Fracture Treatment: Medical Device Set }{ Standard proximal fracture treatment involves Kirschner wires (or "k-wires): sterilized, sharpened, smooth stainless steel pins. It's a well-established method, but not without undue complications in fracture malformation and sequestering within the body (as the wires may migrate away from the fracture site). To prevent these complications, I was part of a team that created a device that externally fastens k-wires to one another and limits their mobility. \\\textbf{Link: }\href{https://seas.yale.edu/news-events/news/students-present-medical-innovations}{https://seas.yale.edu/news-events/news/students-present-medical-innovations} 
\\\vspace{2pt}\textbf{Tech}: MATLAB, Python, CAD}
\vspace{5pt}
\resumeSubItem{Project Rocket: Yale Undergraduate Aerospace Association }{ The rocket team engineers and fabricates YUAA's rocket which competes at the national annual IREC competition in June. I designed and constructed hybrid solid-liquid fuel rockets for competition as a member of Yale Undergraduate Aerospace Association (YUAA). 
\\\vspace{2pt}\textbf{Tech}: MATLAB, CAD}
\resumeSubHeadingListEnd

\end{document}